%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  New template code for TAMU Theses and Dissertations starting Fall 2016.
%
%
%  Author: Sean Zachary Roberson 
%	 Version 3.16.09
%  Last updated 9/12/2016
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                           APPENDIX A 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\phantomsection

\chapter{\uppercase{First Appendix: Notes Made in AAS Wright Editions}}

The table below represents the collection of notes found in the three copies of Wright I located at the American Antiquarian Society. When a title is repeated in a later copy, the term "added" is used. The titles are listed in alphabetical order irrespective of their columns.
% Please add the following required packages to your document preamble:
% \usepackage{longtable}
% Note: It may be necessary to compile the document several times to get a multi-page table to line up properly
\begin{longtable}[c]{|p{5cm}|p{5cm}|p{5cm}|}
\caption{NOTES MADE IN AAS WRIGHT EDITIONS} \\
\hline
\textbf{AAS Backlog 19C 1325} & \textbf{RefT Fiction 05a} & \textbf{RefT Fiction 05b} \\ \hline
\endfirsthead
%
\multicolumn{3}{c}%
{{\bfseries Table \thetable\ continued from previous page}} \\
\hline
\textbf{AAS Backlog 19C 1325} & \textbf{RefT Fiction 05a} & \textbf{RefT Fiction 05b} \\ \hline
\endhead
%
\textbf{Wright I 1939} & \textbf{Wright I 1939} & \textbf{Wright I 1948} \\ \hline
 &  & Abraham Vest. Boston, 1847 (maybe nonfiction) \\ \hline
 & "Adelio" A Journey to Philadelphia; or, Memoirs of Charles Coleman Saunders, An Original Tale. By Adelio. Hartford: Printed by Lincoln \& Gleason, 1804. 72p. 12mo &  \\ \hline
Addison, Alvin. Evelyn Mandeville {[}1837{]} & added & added \\ \hline
 & Abbot, Jacob. McDonner or... Boston, 1839 & added (adds Crocker \& Brewster as publisher and the 283p.) \\ \hline
 & An Adventure in Newbury Park, 1813 (also contains note "omit revisions" on side) &  \\ \hline
 &  & The Adventures of Count D'orveau, A Romance. Philadelphia: published by G.M. \& W. Snider, 1832. 180p. \\ \hline
 &  & Adventure in Vermont, 1813 (noted as omitted as it was a serial extra) \\ \hline
 &  & Aesop Junior in America, NY 1834 ("purposely {[}sic{]} omitted") \\ \hline
 &  & Albert and Eliza. NY 1802 \\ \hline
Alden, Joseph. The Cardinal Flower and Other Tales. Boston Bejnj. Perkins + Co., 1845 &  &  \\ \hline
--. Alicia. Boston: Gleason, 1847. 8vo. 50pp. illus. &  &  \\ \hline
--. Adelaide; or, The Rainy Evening. Boston, 1827 & added &  \\ \hline
--. The Dying Robin. NY 1848 & added & added (noted omitted as a juvenile) \\ \hline
--. The Farmer's Daughter. NY {[}1847{]} &  &  \\ \hline
--. Lawyer's Daughter. NY {[}1847{]} & added &  \\ \hline
 &  & Alden, Joseph. The Old Stone House. NY 1848. 143p. \\ \hline
 &  & Alice or the Victim of Indiscretion. NY 1844. \\ \hline
Allen, Elizabeth. Sketches of Green Mt. Life. Lowell Nathan Dayton 1846 &  &  \\ \hline
Amory, John. H. Almonuc. Boston 1837, 1838 2nd ed. 1840, 1841.  144pp. & added &  \\ \hline
 &  & Andover Husking. Boston: 1842. ("not included by Wright") \\ \hline
 &  & Annette Warington, Sequel to Black Velvet Bracelet. Boston: 1832. p.231 (AAS attributes this to L.H.H. Cleveland in the online catalog) \\ \hline
Waterston-Arthur Lee + Tom Palmer. Boston 1839 & added (as only Arthur Lee \& Tom Palmer). &  \\ \hline
 & Arthur, Timothy Shay. Advice to Young Men. Boston: N. C. Barton, 1849 &  \\ \hline
 & --. Anna Milnor. NY: E. Ferret \& Co. 1845. 92p. &  \\ \hline
Arthur, Timothy Shay. The Banker's Wife. Philadelphia: Peterson {[}1851{]} 104pp. &  &  \\ \hline
--. The Divorced Wife. Phila: Peterson {[}1850{]}. 96pp. & added &  \\ \hline
 & --. I Knew How It Would Be. Boston: 1849 &  \\ \hline
 & --. Life Pictures &  \\ \hline
--. Lucy Sandford. Phila: {[}1848{]} 131 pp. 8vo. &  &  \\ \hline
--. Madeline; or, A Daughter's Love. P {[}1845{]} &  &  \\ \hline
--. Mary Ellis. Phila {[}1850{]} & added &  \\ \hline
 & --. Mary Moreton. Phila: T. B. Peterson, {[}c.1849{]}. 100p. &  \\ \hline
--. The Old Man's Bride & added &  \\ \hline
--. Off-hand Sketches. Phila. 1851 & added &  \\ \hline
 & --. Random Recollections of an Old Doctor. {[}ed. by T.S. Arthur{]}. Baltimore, 1846 &  \\ \hline
 &  & Arthur, Timothy Shay. Sons of Temperance, an offering for 1850. \\ \hline
 &  & --. The Story Book. Philadelphia; New York: 1843 ("juvenile") \\ \hline
 &  & --. Swearing Off and Other Tales. 2v in one. Phila. 1843. ("see The Ruined Family") \\ \hline
--. Tales of Domestic Life. Phila {[}1850{]} & added &  \\ \hline
 &  & --. Tales of Married Life. Phil 1850 \\ \hline
--. The Two Husbands. Phila 1845. & added &  \\ \hline
--. The Two Brides. Phila Peterson {[}1850{]}. 90pp. & added &  \\ \hline
--. The Widow's Children in Farmingdale (part of the Village Doctors and Other Tales) &  &  \\ \hline
--. The Widow Morrison. Balto.:Knight \& Colburn, 1841. & added & added \\ \hline
--. Young Lady at Home. Phila {[}1847{]} &  &  \\ \hline
 &  & Ashland, Aria. Dark Sybil. Boston: 1848. 100p. \\ \hline
Austin, Charles. Frank Marston, 1847. & added &  \\ \hline
 & Albert Simmons. Boston, 1849. 100p. &  \\ \hline
 &  & Ayer, I{[}saiah{]} Winslow. The Hungarian Refugee. Boston: 1850. 99p. ("see letter to L.H. Wright Sept. 14, 1949.") \\ \hline
 & Baker, Mrs. F. M.  Louisa Murray and Other Tales. NY 1846, 129p. & added \\ \hline 
\end{longtable}
