\documentclass[course, english]{Notes}
\usepackage{parskip}
\usepackage{graphicx}
\usepackage{csquotes}
\usepackage{outlines}

\setlength{\parindent}{0cm}
\raggedright
\setcounter{secnumdepth}{5}
\title{Am. Bibliography Oddities}
\date{14}{04}{2017}

\newcommand{\n}{\scalebox{2}{\textbf{\framebox{$\aleph$} } } }

\begin{document}
\section{WRIGHT}
\subsection{Things Not In Wright}
\begin{itemize}
\item{Delany, \textit{Blake, or the Huts of America}}
\item{Whitman, \textit{Franklin Evans}}
\item{Alcott, \textit{Little Women}, and it's sequels \textit{Little Men}, \textit{Jo's Boys}, etc.} The book was originally titled \textit{Good Wives} in England, but that is not included either.
\item{Alcott's short story horror fiction isn't there either.}

\end{itemize}

\subsection{Errors in Wright}
\begin{itemize}

\item{ Jacobs, \textit{Incidents in the Life of a Slave Girl}}
\item{ possible the wrong year for Warner's \textit{Wide, Wide World}? \textbf{double check}}
\item Solomon Northup, \textit{Twelve Years a Slave}, 1853. Entry 1799
\end{itemize}

\subsection{Oddities in Wright}
\begin{itemize}

\item{ Pg. 132 of Vol. 1, no.977, \textbf{DELETE.}. I dunno.}
\item{ References the \textit{Key} in the entry for \textit{Uncle Tom's Cabin}}
\item Dickens' \textit{Edwin Drood} is in here, listed under the corrections. 750a. Wright American Fiction Project then puts the entry in its database. 
\item Fanny Fern listed under her real name- Sara Payson Parton, entries 1845-1849.
\item William Makepiece Thackery in included with 2 other authors- Good Stories vol. 4
\item entry 2282- Deacon Snowball and his Comic Lectures
\end{itemize}

\section{BAL-including Epitome by Winship and Eppard}
\subsection{errors}
\begin{outline}
\1 Lydia Marie Child tagged as author of \textit{Incidents}, no.3192

\1 Blanck does not mention the narrative chronology or even the assumed pairing of stories in Cooper's Leatherstocking Tales: 
\begin{table}
\centering
	{\begin{tabular}{ |c|c|c|c| }
			\hline
			 Deerslayer & 1841 & 1740-1755\\
			Last of the Mohicans & 1826 & 1757\\
			Pathfinder &  1840 & 1758-1759\\
			Pioneers &  1823 & 1793\\
			Prairie & 1827 & 1804\\
			\hline
	\end{tabular}}
\end{table}

\1 Same goes for Mark Twain, narrative connections among Tom Sawyer/Huck Finn works are ignored.
	\2 Alcott, however, seems to get something else- \textit{Little Women} and \textit{Little Men} are not connected, but \textit{Jo's Boys} is labeled as a sequel to \textit{Little Men}

\subsection{Omitted Authors}
E.D.E.N. Southworth
Rebecca Harding Davis
Fanny Fern (Sara Payson Parton)
Timothy Shay Arthur
William James
Edward Everett Hale

\end{outline}


\end{document}